Weak interspecific interactions in a sagebrush steppe: evidence from observations, models, and experiments

### 2017-01-13 removals/manuscript/removal_ms.tex
Cover letter and formatting

\date{Last compile: \today}

@@

\textbf{\large{Keywords:}} Coexistence, competition, integral projection model.

@@

\smallskip \textbf{Article type:} Letter

\smallskip \textbf{Authorship statement:} PBA and ARK designed the experiment and supervised data collection with the help of JBT, PBA, SPE, GH and BT analyzed data, PBA wrote the first draft of the manuscript and all authors contributed to editing.
\smallskip

\setlength{\parindent}{8ex}

@@

>>>>

% \date{Last compile: \today}

@@

\textbf{\large{Keywords:}} Coexistence, competition, integral projection model, removal experiment, sagebrush steppe.

@@

\smallskip \textbf{Article type:} Standard Paper

@@

\section*{Author contributions}

PBA and ARK designed the experiment and supervised data collection with the help of JBT, PBA, SPE, GH and BT analyzed data, PBA wrote the first draft of the manuscript and all authors contributed to editing.
